02_DESeq_characterization

### 2019-08-27 analysis/03_DESeq2_characterization.Rmd
now with candidate gene heatmaps

## heamap with minimum pvalue

@@

#makepheatmap(dds.female_hypothalamus, colDataFH, "female hypothalamus")
#makepheatmap(dds.female_pituitary, colDataFP, "female pituitary")
#makepheatmap(dds.female_gonad, colDataFG, "female gonad")
#makepheatmap(dds.male_hypothalamus, colDataMH,  "male hypothalamus")
#makepheatmap(dds.male_pituitary, colDataMP, "male pituitary")
#makepheatmap(dds.male_gondad, colDataMG, "male gonad")
```
## plot candidate genes

>>>>

## heamap of candidate genes

@@

makepheatmap(dds.female_hypothalamus, colDataFH, "female hypothalamus")
makepheatmap(dds.female_pituitary, colDataFP, "female pituitary")
makepheatmap(dds.female_gonad, colDataFG, "female gonad")
makepheatmap(dds.male_hypothalamus, colDataMH,  "male hypothalamus")
makepheatmap(dds.male_pituitary, colDataMP, "male pituitary")
makepheatmap(dds.male_gondad, colDataMG, "male gonad")
```
## plot candidate genes
